Analytic consideration of the society by itself

### 2017-11-14 latex/nuvem/nuvem1.tex
pequena correcao em nuvem1

The Anthropological Physics is concerned
with the observation of natural
phenomena in the social structures
of the observer and has been
considered in~\cite{an,an2,tese}.
Comte talked about anthropological physics,
but it had the sense which physical (or biological or natural)
anthropology has, which is a branch of anthropology
(the other is social anthropology).
Anthropological physics, in the sense we use and understand correct,
is physics (research on the natural phenomena mainly of complex networks)
with anthropological aspects.
The writing and study of diaries is a traditional ethnographic asset,
which resembles the collection and study of one's data by the person itself,
social data.
The current guidelines are centered on keeping the process open,
using free and open source tools and file formats,
and publicly accessible repositories of software, gadgets, data, writings, etc;
while gathering and studying the social data related to the researcher
(and other data if needed and afterwards).~\cite{an,an2,imp,tese}

>>>>

The Anthropological Physics is concerned
with the observation of natural
phenomena in the social structures
of the observer and has been
considered in~\cite{an,an2,tese}.
Comte talked about anthropological physics,
but it had the sense which physical
anthropology has, which is a branch of anthropology
(the other is sociocultural anthropology).
Anthropological physics, in the sense we use and understand correct,
is physics (research on the natural phenomena mainly of complex networks)
with anthropological aspects.
The writing and study of diaries is a traditional ethnographic asset,
which resembles the collection and study of one's data by the person itself,
social data.
The current guidelines are centered on keeping the process open,
using free and open source tools and file formats,
and publicly accessible repositories of software, gadgets, data, writings, etc;
while gathering and studying the social data related to the researcher
(and other data if needed and afterwards).~\cite{an,an2,imp,tese}
